### 2015-02-20 proofs.tex
writeup for n=0 mod 3 complete

Then $\frac{f_1-s_{0a}f_1}{x_a}=-f_a/x_a=x_a^2+c \left(\sum_{i=1}^{n-1} x_i(x_i-x_a)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.

@@

@@

A simple algebraic manipulation lets us see that $f_a=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$. %todo
We also note that $\sum_{i=1}^{n-1} f_i = (c^2+2)\sum_{i=1}^{n-1} x_i^3 = (c^2+2)\left(\sum_{i=1}^{n-1} x_i \right)^3$ %todo
Therefore if $f_1(x) = \dots = f_{n-1}(x)=0$, we see that $\sum_{i=1}^{n-1} x_i = 0$. %notational fix?
Modulo this new relation, we see that $f_a=x_a\left(-x_a^2+\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$. Therefore if $f_a=0$ for all $a$, we see that for each $a$, either $x_a=0$ or $x_a$ is a square root of $C=\sum_{1 \le i < j  \le n-1} 2cx_ix_j$. If $C=0$ or $C$ has no square roots, then all the $x_a$ are 0 and we are done; so we assume $C$ has two square roots which are additive inverses of each other. Then each pair $x_ix_j$ either multiply to $\pm C$ or $0$, so $C=2cmC$ for some integer $m$. Then $(1+cm)C=0$; if $C \ne 0$, then $1+cm=0$; however, $m$ is an integer, so this is impossible. Therefore $C=0$, so all the $x_a$ are $0$.

>>>>

Then $\frac{f_1-s_{0a}f_1}{x_a}=f_a/x_a=-x_a^2-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_a)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$.

@@

We calculate $\partial_2f_1$:

\begin{align*}
\partial_2f_1&=\partial_2\left(-x_1^3+c \left(\sum_{i=1}^{n-1} x_1x_i(x_1-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_1\right)\right)\\
&=\partial_2\left(-x_1^3+c \left(\sum_{i=3}^{n-1} x_1x_i(x_1-x_i)\right)+cx_1x_2(x_1-x_2)+c^2 \left(\sum_{i \ne 2}\sum_{j \ne 2} x_ix_jx_1\right)+2c^2\left(\sum_{i \ne 2}x_ix_1x_2\right)+c^2x_2^2x_1\right)\\
&=cx_1^2-2cx_1x_2+2c^2\left(\sum_{i \ne 2}x_ix_1\right)+2c^2x_2x_1\\
&=cx_1^2+cx_1x_2+2c^2\left(\sum_{i=1}^{n-1}x_ix_1\right)\\
\end{align*}

Let $G_1=\frac{f_1-s_{12}f_1}{x_2-x_1}, G_2=\frac{f_1-s_{02}f_1}{x_2}$. If $c(G_1+G_2)=\partial_2f_1$, then $D_2f_1=0$.

\begin{align*}
G_1+G_2&=\frac{f_1-s_{12}f_1}{x_2-x_1}+\frac{f_1-s_{02}f_1}{x_2}\\
&=(x_1-x_2)^2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i)\right)-c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)-
x_2^2-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_2)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)\\
&=x_1^2+x_1x_2+x_2^2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i)\right)-
x_2^2-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_2)\right)\\
&=x_1^2+x_1x_2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i)\right)-c \left(\sum_{i=1}^{n-1} x_i(x_i-x_2)\right)\\
&=x_1^2+x_1x_2-c \left(\sum_{i=1}^{n-1} x_i(x_1+x_2-x_i+x_i-x_2)\right)\\
&=x_1^2+x_1x_2-c \left(\sum_{i=1}^{n-1} x_ix_1\right)\\
\end{align*}

Then we see easily that $\partial_2f_1=cG_1+cG_2$, so $D_2f_1=0$ as desired.

@@

Recall $f_a = -x_a^3+c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)$.

We also note that $\left(\sum_{i=1}^{n-1} x_i \right)^2= \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)$, and $\left(\sum_{i=1}^{n-1} x_i \right)^2+\sum_{1 \le i < j \le n-1} x_ix_j = \sum_{i=1}^{n-1} x_i^2$ modulo $3$.

Therefore:

\begin{align*}
f_a &= -x_a^3+c \left(\sum_{i=1}^{n-1} x_ax_i(x_a-x_i)\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)\\
&= -x_a^3+c \left(\sum_{i=1}^{n-1} x_a^2x_i-x_ax_i^2\right)+c^2 \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_jx_a\right)\\
&= -x_a^3+cx_a^2 \left(\sum_{i=1}^{n-1} x_i\right) -cx_a\left( \sum_{i=1}^{n-1} x_i^2\right)+c^2x_a \left(\sum_{i=1}^{n-1} \sum_{j=1}^{n-1} x_ix_j\right)\\
&= -x_a^3+cx_a^2 \left(\sum_{i=1}^{n-1} x_i\right) +2cx_a\left(\sum_{i=1}^{n-1} x_i \right)^2+2cx_a\left(\sum_{1 \le i < j \le n-1} x_ix_j\right)+c^2x_a\left(\sum_{i=1}^{n-1} x_i \right)^2\\
&=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)
\end{align*}

We see that $f_a=-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$.

We now consider the sum of the $f_a$:

\begin{align*}
\sum_{a=1}^{n-1} f_a &= \sum_{a=1}^{n-1}\left(-x_a^3+c x_a^2\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)x_a\left(\sum_{i=1}^{n-1} x_i\right)^2+x_a\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)\right)\\
 &= \left(\sum_{a=1}^{n-1}-x_a^3\right)+c\left(\sum_{a=1}^{n-1}x_a^2\right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{a=1}^{n-1}x_a\right)\left(\sum_{i=1}^{n-1} x_i\right)^2+\left(\sum_{a=1}^{n-1}x_a\right)\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)\\
  &= 2\left(\sum_{i=1}^{n-1}x_i^3\right)+c\left(\sum_{i=1}^{n-1}x_i^2\right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{i=1}^{n-1} x_i\right)^2+\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)\\
    &= 2\left(\sum_{i=1}^{n-1}x_i^3\right)+c\left(\left(\sum_{i=1}^{n-1} x_i \right)^2+\left(\sum_{1 \le i < j \le n-1} x_ix_j\right) \right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{i=1}^{n-1}x_i\right)^3+\\&2c\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{1 \le i < j  \le n-1} x_ix_j\right)\\
        &= 2\left(\sum_{i=1}^{n-1}x_i^3\right)+c\left(\sum_{i=1}^{n-1} x_i \right)^3+c\left(\sum_{1 \le i < j \le n-1} x_ix_j\right)\left(\sum_{i=1}^{n-1} x_i \right)+(c^2+2c)\left(\sum_{i=1}^{n-1}x_i\right)^3+\\&2c\left(\sum_{i=1}^{n-1}x_i\right)\left(\sum_{1 \le i < j  \le n-1} x_ix_j\right)\\
        &=(c^2+2)\left(\sum_{i=1}^{n-1} x_i\right)^3\\
\end{align*}

We see that $\sum_{a=1}^{n-1} f_a=  (c^2+2)\left(\sum_{i=1}^{n-1} x_i \right)^3$.

Therefore if $f_1(x) = \dots = f_{n-1}(x)=0$, we see that $\sum_{i=1}^{n-1} x_i = 0$. Modulo this new relation, we see that $f_a=x_a\left(-x_a^2+\sum_{1 \le i < j  \le n-1} 2cx_ix_j\right)$. Therefore if $f_a=0$ for all $a$, we see that for each $a$, either $x_a=0$ or $x_a$ is a square root of $C=\sum_{1 \le i < j  \le n-1} 2cx_ix_j$. If $C=0$ or $C$ has no square roots, then all the $x_a$ are 0 and we are done; so we assume $C$ has two square roots which are additive inverses of each other. Then each pair $x_ix_j$ either multiply to $\pm C$ or $0$, so $C=2cmC$ for some integer $m$. Then $(1+cm)C=0$; if $C \ne 0$, then $1+cm=0$; however, $m$ is an integer, so this is impossible. Therefore $C=0$, so all the $x_a$ are $0$.
